Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models

### 2020-06-09 analysis/paper/paper.Rmd
added needed line to load habitat data (hab_data)

```{r load-data}
fish_hab = read_rds("../data/derived_data/fish_hab.rds")
hab_dict = read_rds("../data/derived_data/hab_dict.rds")
qrf_data = read_rds("../data/derived_data/qrf_data.rds")
dens_offset = read_rds("../data/derived_data/dens_offset.rds")
qrf_mod = read_rds("../data/derived_data/qrf_mod.rds")
sel_hab_mets = read_rds("../data/derived_data/sel_hab_mets.rds")
gaa_covars = read_rds("../data/derived_data/gaa_covars.rds")
mod_data_weights = read_rds("../data/derived_data/mod_data_weights.rds")
all_preds = read_rds("../data/derived_data/all_preds.rds")
spawn_rec_params = read_rds("../data/derived_data/spawn_rec_params.rds")
model_svy_df = read_rds("../data/derived_data/model_svy_df.rds")
champ_wtsds = read_rds("../data/derived_data/champ_wtds.rds")

>>>>

```{r load-data}
hab_data = read_rds("../data/derived_data/hab_data.rds")
fish_hab = read_rds("../data/derived_data/fish_hab.rds")
hab_dict = read_rds("../data/derived_data/hab_dict.rds")
qrf_data = read_rds("../data/derived_data/qrf_data.rds")
dens_offset = read_rds("../data/derived_data/dens_offset.rds")
qrf_mod = read_rds("../data/derived_data/qrf_mod.rds")
sel_hab_mets = read_rds("../data/derived_data/sel_hab_mets.rds")
gaa_covars = read_rds("../data/derived_data/gaa_covars.rds")
mod_data_weights = read_rds("../data/derived_data/mod_data_weights.rds")
all_preds = read_rds("../data/derived_data/all_preds.rds")
spawn_rec_params = read_rds("../data/derived_data/spawn_rec_params.rds")
model_svy_df = read_rds("../data/derived_data/model_svy_df.rds")
champ_wtsds = read_rds("../data/derived_data/champ_wtds.rds")
